---
title: "Homework: First Steps with GitHub in RStudio"
author: "Instructions"
format: html
execute:
  echo: true
  warning: false
  message: false
---

## Overview

In this assignment you will learn how to connect **RStudio**, **Git**, and **GitHub** while working inside a **Quarto project**.
These tools form the foundation of a modern data science workflow.
You will create a small Quarto project, track your work using Git commits, and publish the project to GitHub.
The goal of this assignment is to practice the **workflow**, not to perform complex analysis.

## 1) Connect GitHub and RStudio

You should confirm that Git is enabled in RStudio.
See the handout on **Linking GitHub with RStudio**.

## 2) Clone the Repo



Go to GitHub and create a new repository.

Use the exact repository name:

Add a short description such as:

> My first GitHub project using RStudio and Quarto.

Set the repository to **Public**.

------------------------------------------------------------------------

## 2) Create the RStudio Project

Open **RStudio** and create a project connected to GitHub.

Steps:

1.  File → New Project
2.  Version Control
3.  Git
4.  Paste the repository URL from GitHub
5.  Choose a location on your computer

Your project should now contain a **Git tab** in RStudio.

------------------------------------------------------------------------

## 3) Create Your Quarto Document

Create a file called:

Your document must include the following sections.

### Introduction

Write **1–2 paragraphs** explaining the purpose of the assignment and what you are learning.

### Data Summary

Use R code to summarize a built-in dataset such as:

-   `mtcars`
-   `iris`
-   `ToothGrowth`

Example:

```{r}
summary(mtcars)
```

```{r}
library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(
    title = "Miles per Gallon vs Weight",
    x = "Weight",
    y = "Miles per Gallon"
  )
```

Write at least 150 words answering the following:

What was easiest about using GitHub in RStudio?

What was confusing or difficult?

Why might Git be useful for data science projects?

## 4) Render the Document

Your project folder should now contain an HTML file.

Confirm that the document renders without errors.

## 5) Commit Your Work

You must make at least three commits during this assignment.

Each commit should represent a meaningful step.

Example commit sequence:

Write clear commit messages describing what changed.

## 6) Push to GitHub

Push your commits to GitHub from RStudio.

After pushing, check your repository online.

Your repository should contain:

index.qmd

rendered HTML file

commit history

## 7) Submit

Submit the URL of your GitHub repository.

Example format:

https://github.com/username/github-first-steps
